\chapter{To do list}
\begin{itemize}
    \item \sout{Write Introduction}
    \item \sout{Write Different Number of Substractions}
    \item \sout{Explain Analytical Bounds on the Spectrum }
    \item \sout{Finish introduction non abelian }
    \item \sout{Explain n infinity }
    \item \sout{Write positivity bounds in the forward limit}
    \item \sout{Write ww bounds }
    \begin{itemize}
        \item \sout{intro} 
        \item \sout{Standard Model}
        \item \sout{Beyond the Standard Model}
        \item \sout{Odd Substractions}
    \end{itemize}
    \item \sout{Write trumpets}
    \item Write discussion
    \item Write Conventions 
    \item \sout{Make bibliography work}
    \item Choose title
    \item Make figures
    \item Add references
    \item Add citations
    \item \sout{Github workflow}
    \item \sout{Add number of structures}
\end{itemize}

General question: understand whether you can connect IR physics to behaviours at high energies (something stronger than Froissart). Scalars: -2 and 0 substractions. Spin 1: more complicated. We do it with flavour. We tried to do it systematically (a bit technical with respect to the rest, a way to build the amplitude without the lagrangian). We looked at a specific amplitude to see how this works.
\begin{itemize}
    \item Parameters of the lagrangian 
    \item If you write down operators these changes are associated to higher order ops (to separate cubic from quartic we need something stronger), this is a phenomenological approach.
    \item Difference: we are working with an EFT. For our theory is ok if it groes like s, we are being more tolerant.
\end{itemize}

Summary:
No absolute statements independent of any operator. What motivates? Like we have them for graviton and gravitino.

\begin{Todo}
    0 sdr: se anula toda la amplitud??? Here we can talk of \textbf{tunning}. 
\end{Todo}

With dim 6 everything is about.

Somehow, this is telling us that this is similar to the 0 substractions.

\begin{Todo}
    Resaltar gráficas no permitidas!
\end{Todo}

Conclussions: within the bounds that we use, no absolute statements on the spectrum. No direct link between 0 sdr and 1 sdr and the spectrum. In both cases, we have some nice statemets (minimum setup), but they are compromised when adding the dim 6 (missing some bounds OR there are not conclussions to be drawn). Once you work in a eft (contrary to what sm people were doing), you can always tune things that is fine, although we have a stronger tool it seems that it is not enough to find a solid link between the spectrum and the uv behaviour.

In the SM eft, the 3 dimension 6 ops that enter in ww scattering (the only 3, there are 60 but redundancies).