\chapter{Applications to $WW$ scattering}
\label{chap:ww}

We now turn to the process $W^+ W^- \to W^+ W^-$.  
In this configuration, the $s \leftrightarrow u$ crossed amplitude has the same color configuration, so it is not necessary to study additional scattering channels with different external states.

Our aim is to derive constraints on deviations from the Standard Model under different assumptions about the number of subtractions. We begin by considering a setup closely resembling the Standard Model, but with couplings and masses treated as independent parameters rather than fixed by electroweak symmetry breaking. Under different assumptions about the high-energy behaviour of the amplitude, we will obtain constraints on these parameters.

We will then extend the analysis by including dimension-six beyond-the-Standard-Model (BSM) operators and examine how the resulting constraints are modified.

\begin{Todo}
    Explicar el setup. No tengo ni idea de cómo hacerlo... 
    \begin{itemize}
        \item Before symmetry breaking
        \item Cambiar acoplamientos 
        \item Sacar fotón $\rightarrow$ $\cos \theta = 1, \sin \theta = 0$
    \end{itemize}
\end{Todo}

\section{Beyond the Standard Model}

\begin{Todo}
    No me gusta nada el título de esta sección
\end{Todo}

\begin{Todo}
    Explicar cambio acoplamientos y masas
\end{Todo}

First, we assume that the scattering amplitude satisfies $0$-th substracted dispersion relations. This requirement is equivalent to demanding that the amplitude vanishes in the high-energy limit, \( s \to \infty \).

Under this assumption, the relevant arc coefficients are:
\begin{align}
    a_0^{(00)} &= -6 g_Z^2 + g_W^2 \left[ 5 + g_h^2 \left( 2 - \frac{m_h^2}{m^2} \right) \right] 
    + \frac{g_Z^2}{m^4 m_Z^2} \left(-4m^6 - 2m^2 m_Z^4 + m_Z^6 \right), \\
    a_1^{(00)} &= 0, \\
    a_2^{(00)} &= \frac{-g_W^2 + g_Z^2}{m^4}, \\
    a_0^{(++)} &= 2g_W^2 - \frac{g_Z^2 (2m^2 + m_Z^2)}{m_Z^2}, \\
    a_1^{(++)} &= - \frac{g_Z^2}{m_Z^2}, \\
    a_2^{(++)} &= 0.
\end{align}

From the positivity of the twice-subtracted arc, \( a_2^{(00)} \geq 0 \), one obtains
\[
\frac{g_Z^2}{g_W^2} \geq 1,
\]
which provides a lower bound on the coupling of the \( Z \) boson to the \( W \) boson.

Combining this with the positivity of the 0-th substracted arc, \( a_0^{(++)} \geq 0 \), yields
\[
m_Z^2 \geq 2 m^2.
\]
This bound already excludes the Standard Model configuration, where \( m_Z^2 = m^2 \).
To complete the analysis, we use the relation between once- and 0-th substracted arcs,
\[
\left| a_1^{(++)} \right| (\Lambda^2 - 2m^2) \leq a_0^{(++)}.
\]
This inequality leads to two distinct regimes:
\[
\begin{cases}
    \dfrac{g_Z^2}{g_W^2} \leq 2 
    \;\Rightarrow\;
    \dfrac{m_Z^2}{\Lambda^2} \geq \dfrac{ \frac{g_Z^2}{g_W^2} }{2 - \frac{g_Z^2}{g_W^2}}, \\[1em]

    \dfrac{g_Z^2}{g_W^2} \geq 2 
    \;\Rightarrow\;
    \dfrac{m_Z^2}{\Lambda^2} \leq \dfrac{ \frac{g_Z^2}{g_W^2} }{2 - \frac{g_Z^2}{g_W^2}} < 0.
\end{cases}
\]
The second regime, \( g_Z^2 \geq 2 g_W^2 \), is clearly inconsistent. In the first regime, \( g_Z^2 \leq 2 g_W^2 \), there appears to be a viable window. However, combining this with the bound \( g_Z^2 \geq g_W^2 \) implies
\[
m_Z^2 \geq \Lambda^2,
\]
this is the \( Z \)-boson resonance would lie above the cutoff. This is problematic, as the effective theory cannot reliably describe physics above \( \Lambda \). This is summarized in figure 
\begin{Todo}
    Añadir figura
\end{Todo}
Therefore, the process under consideration is not consistent with unsubtracted dispersion relations. However, it remains compatible with twice-subtracted dispersion relations, provided that \( g_Z^2 \geq g_W^2 \).

This condition is reminiscent of the role of the three-point coupling in ensuring the cancellation of the \( s^2 \) growth in the scattering amplitude for \( W^+_L W^-_L \rightarrow W^+_L W^-_L \). Such a cancellation is required by gauge invariance and follows from Ward identities \autocite{Lee:1977eg}.

\section{Higher Order Operators}
We are interested now in understanding 

\section{Odd Number of Substractions}
